R Notebook

### 2018-09-18 study2/vmb_model_preds.Rmd
added files

plot_processed_predictions <- function(processed_predictions) {
  require(dplyr)
  require(ggplot2)
  plt1 <- processed_predictions %>%
    mutate(
           UL = observed + std_error*1.96,
           LL = observed - std_error*1.96
           ) %>%
    ggplot(aes(x=predicted, y = observed, ymin = LL, ymax=UL)) +
    geom_errorbar(color="grey", width=0) +
    geom_point() +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
    theme_bw() +
    theme(aspect.ratio = 1)

  plt2 <- processed_predictions %>% 
    # left_join(obs_error, by = "scale") %>%
    group_by(scale) %>%
    gather(type, change_score, observed, predicted) %>%
    mutate(std_error = ifelse(type == "observed", std_error, NA )) %>%
    mutate(
           UL = change_score + std_error*1.96,
           LL = change_score - std_error*1.96
           ) %>%
    ggplot(aes(y = reorder(scale, change_score),
               x = change_score,
               xmax = UL, 
               xmin = LL, 
               color = type)) +
    geom_point(shape=17, size=3) +
    geom_errorbarh(height=0) +
    theme_bw()
    # theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

# conceptual illustration

```{r}
p_x <- rbeta(100, 2, 2)
p_y_x0 = .4
p_y_x1 = .8

p_y = rethinking::rbeta2(100, p_x*p_y_x1 + (1-p_x)*p_y_x0, 100)

plot(p_x, p_y)

df <- data.frame(x=p_x, y=p_y)
df %>%
  rename(`p(fire)` = x,
         `p(smoke)` = y) %>%
  ggplot(aes(x=`p(fire)`, y = `p(smoke)`)) +
  geom_point() +
  theme_bw(base_size = 24)
```

# correlation matrix

```{r}
# borrowing code from
# http://www.sthda.com/english/wiki/ggplot2-quick-correlation-matrix-heatmap-r-software-and-data-visualization

reorder_cormat <- function(cormat){
  # Use correlation between variables as distance
  dd <- as.dist((1-cormat)/2)
  hc <- hclust(dd)
  cormat <-cormat[hc$order, hc$order]
}

# Get lower triangle of the correlation matrix
get_lower_tri<-function(cormat){
  cormat[upper.tri(cormat)] <- NA
  return(cormat)
}
# Get upper triangle of the correlation matrix
get_upper_tri <- function(cormat){
  cormat[lower.tri(cormat)]<- NA
  return(cormat)
}

corr_plot <- d_bn %>%
  cor() %>%
  reorder_cormat() %>%
  # get_lower_tri() %>%
  reshape2::melt(na.rm=TRUE) %>%
  ggplot(aes(x=Var1, y = Var2, fill = value)) +
  geom_tile(color = "white") +
  geom_tile() +
  geom_text(aes(label=round(value,2)), size=6*.35) +
  scale_fill_distiller(type="div", palette = "RdYlBu") +
  # scale_fill_viridis_c(limit = c(-1,1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=.85)) +
  theme(aspect.ratio = 1) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(fill="corr.")

ggsave("corrplot.png", corr_plot, dpi=320, height=5,width=5)
```

@@

preds_cog <- predict_change_scores(cog_model,
                                           data.frame(interv = 0),
                                           data.frame(interv = 1),
                                           nodes_to_predict,
                                           iter = 1e5*2.5
                                           )

@@

scores_cog <- score_predictions(preds_cog)

plt1 <- plots_cog$corr_plot +
  geom_text(
    aes(
      label = ifelse(observed == preds_cog[which(preds_cog$scale == "diseaseSevere"), "observed"],
        as.character(scale), ""
      )
    ),
    hjust = 1.1, vjust = 0
  ) +
  geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
    as.character(scale), ""
  )), hjust = 1.1, vjust = 0) +
  theme(aspect.ratio = 1) +
  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
  annotate("text", 
           x = .25, 
           y = -.2, 
           label = paste("italic(R)^2 == ", round(scores_cog$r_squared,3)), 
           parse = TRUE,
           size=18*.35
          ) +
  theme_bw(base_size=18)

plt2 <- plots_cog$means_plot +
  labs(x="Change score", y="Belief Scale") +
  theme_bw(base_size=18) +
  theme(legend.position = "bottom")

ggsave("plot.png", plot = plt1, dpi=320, width=4, height=4)
ggsave("plot2.png", plot = plt2, dpi=320, width=6, height=4)

@@

## "Non-mental" model

@@

scores_causal <- score_predictions(preds_causal)

plt3 <- plots_causal$corr_plot +
  geom_text(
    aes(
      label = ifelse(observed == preds_causal[which(preds_causal$scale == "diseaseSevere"), "observed"],
        as.character(scale), ""
      )
    ),
    hjust = 1.1, vjust = 0
  ) +
  # geom_text(aes(label = ifelse(observed == preds_cog[which(preds_cog$scale == "overpar"), "observed"],
  #   as.character(scale), ""
  # )), hjust = 1.1, vjust = 0) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  theme(aspect.ratio = 1) +
  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
  annotate("text", 
           x = .25, 
           y = -.2, 
           label = paste("italic(R)^2 == ", round(scores_causal$r_squared,3)), 
           parse=TRUE,
           size=14*.35
          ) +
  theme_bw(base_size=18)

# plots_causal$means_plot +
#   labs(x="Change score", y="Belief Scale") +
#   theme_bw(base_size=18)

ggsave("plot3.png", plot = plt3, dpi=320, width=4, height=4)
```

@@

Here we can pretend that expectations for the intervention materials are set by each of the 14 beliefs, and compare the accuracy of the resulting models' predictions. We should also ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.

```{r}
predict_change_scores_pipe <- partial(predict_change_scores,
                                      data0 = data.frame(interv = 0),
                                      data1 = data.frame(interv = 1),
                                      nodes_to_predict = nodes_to_predict,
                                      iter = 1e5
                                      )

@@

@@

model_compare <- tibble(
  model_name = all_beliefs,
  model = unlist(belief_targets_models)
  ) %>%
    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
    mutate(scores = map(proc_preds, score_predictions_boot))

model_compare2 <- model_compare %>%
    mutate(
      rmse = map(scores, ~ sapply(.x, function(z){z$rmse})),
      r_squared = map(scores, ~ sapply(.x, function(z){z$r_squared}))
      ) %>%
  gather(metric, value, rmse, r_squared) %>%
  mutate(
    mean_value = map_dbl(value, mean),
    se_value = map_dbl(value, sd)
    )

plt_models <- model_compare2 %>%
  mutate(
    UL = mean_value + se_value,
    LL = mean_value - se_value
  ) %>%
  ggplot(aes(x = reorder(model_name, -mean_value), y = mean_value, ymin = LL, ymax = UL)) +
  geom_pointrange() +
  theme_bw(base_size=18) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~metric, scales="free") +
  labs(x="Targetted belief", y = "Score")

ggsave("plot_models.png", plot = plt_models, dpi=320, width=12, height=6)
```

@@

scores_cog2 <- score_predictions(preds_cog2)

plt4 <- plots_cog2$corr_plot +
  geom_text(
    aes(
      label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "diseaseSevere"), "observed"],
        as.character(scale), ""
      )
    ),
    hjust = 1.1, vjust = 0
  ) +
  geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "overpar"), "observed"],
    as.character(scale), ""
  )), hjust = 1.1, vjust = 0) +
    geom_text(aes(label = ifelse(observed == preds_cog2[which(preds_cog2$scale == "infantImmWeak"), "observed"],
    as.character(scale), ""
  )), hjust = 1.1, vjust = 0) +
  # geom_abline(intercept = 0, slope = 1, linetype = "dashed", color="grey") +
  # geom_errorbar(aes(ymin = LL, ymax=UL)) +
  theme(aspect.ratio = 1) +
  coord_cartesian(xlim=c(-.25,.35), ylim=c(-.25,.35)) +
  annotate("text", 
           x = .25, 
           y = -.2, 
           label = paste("italic(R)^2 == ", round(scores_cog2$r_squared,3)), 
           parse=TRUE,
           size=14*.35
          )

plots_cog2$means_plot +
  labs(x="Change score", y="Belief Scale")

ggsave("plot4.png", plot = plt4, dpi=320, width=4, height=4)
```

@@

>>>>

plot_processed_predictions <- function(processed_predictions) {
  require(dplyr)
  require(ggplot2)
  plt1 <- processed_predictions %>%
    ggplot(aes(x=predicted, y = observed)) +
    geom_point() +
    theme_bw() +
    theme(aspect.ratio = 1)

  plt2 <- processed_predictions %>% 
    # left_join(obs_error, by = "scale") %>%
    group_by(scale) %>%
    gather(type, change_score, observed, predicted) %>%
    mutate(std_error = ifelse(type == "observed", std_error, NA )) %>%
    mutate(
           UL = change_score + std_error*1.96,
           LL = change_score - std_error*1.96
           ) %>%
    ggplot(aes(y = reorder(scale, change_score),
               x = change_score,
               xmax = UL, 
               xmin = LL, 
               color = type)) +
    geom_point(shape=17, size=3) +
    geom_errorbarh(height=0) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

@@

preds_cog <- predict_change_scores(cog_model,
                                           data.frame(interv = 0),
                                           data.frame(interv = 1),
                                           nodes_to_predict,
                                           iter = 1e5
                                           )

@@

plots_cog$corr_plot
plots_cog$means_plot

score_predictions(preds_cog)

@@

## "Causal" model

@@

plots_causal$corr_plot
plots_causal$means_plot

score_predictions(preds_causal)
```

@@

Here we can pretend that expectations for the intervention materials are set by each of the 14 beliefs, and compare the accuracy of the resulting models' predictions.

@@

r_belief_targets <- lapply(all_beliefs, function(b){

@@

  preds <- predict_change_scores(cog_model,
                                             data.frame(interv = 0),
                                           data.frame(interv = 1),
                                             nodes_to_predict,
                                             iter = 1e5
                                             )

  preds <- process_predictions(preds, obs_data)
  score_predictions(preds)
  }
)

names(r_belief_targets) <- all_beliefs

r_belief_targets %>% 
  data.frame() %>%
  gather(id, value) %>% 
  mutate(
    belief = gsub("\\.(.*)","",id), 
    metric = gsub("(.*)\\.","",id)
    ) %>%
  select(-id) %>%
  ggplot(aes(x = belief, y = value)) +
  geom_point() +
  facet_wrap(~ metric, scales = "free") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

By all metrics disease severity gives the best fit, with disease rarity in second place. Both seem highly plausible as targets of the intervention. None of the other beliefs come close.

# Playing with edge directions

The direction of three edges were set arbitrarily in our original cogsci model. Here I examine what happens if we change their directions (comparing the original model with the 6 other possible models).

```{r, message=FALSE, warning=FALSE}
# here I can swap things around
mynet <- net.struct

mynet1 <- reverse.arc(mynet, "hb","nat") # this might be the best
mynet2 <- reverse.arc(mynet, "vaccStrain","vaccDanger") 
mynet3 <- reverse.arc(mynet1, "vaccStrain","vaccDanger")
mynet4 <- reverse.arc(mynet2, "vaccTox","vaccDanger")
mynet5 <- reverse.arc(mynet3, "vaccTox","vaccDanger")

possible_dags <- list(
  mynet,
  mynet1,
  mynet2,
  mynet3,
  mynet4,
  mynet5
  )

r_dag_comparisons <- lapply(possible_dags, function(dag){

  dag_model <- write_jags_model(bnlearn_to_df(dag), d_bn) %>% suppressWarnings()

  dag_model <- add_node(dag_model, glm_to_jags_eq(interv_fit))

  preds <- predict_change_scores(dag_model,
                                             data.frame(interv = 0),
                                           data.frame(interv = 1),
                                             nodes_to_predict,
                                             iter = 1e5*2.5
                                             )

  preds <- process_predictions(preds, obs_data)
  score_predictions(preds)
  }
)

names(r_dag_comparisons) <- c(
  "original",
  "swap_hb_nat",
  "swap_vs_vd",
  "swap_hb_nat_vs_vd",
  "swap_vs_vd_vt_vd",
  "swap_hb_nat_vs_vd_vt_vd"
)

r_dag_comparisons %>% 
  data.frame() %>%
  gather(id, value) %>% 
  mutate(
    dag = gsub("\\.(.*)","",id), 
    metric = gsub("(.*)\\.","",id)
    ) %>%
  select(-id) %>%
  ggplot(aes(x = dag, y = value)) +
  geom_point() +
  facet_wrap(~ metric, scales = "free") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

This analysis doesn't hugely favor any of the models, and even seems sensitive to error in the predictions, so I've ramped mcmc sampels up to 250k.

@@

plots_cog2$corr_plot
plots_cog2$means_plot

score_predictions(preds_cog2)
```

@@

# Binning participants

One idea we had was to predict change scores for different bins of participants. The obvious binning variable to me is disease severity. Here I'm binning participants by disease severity quartile (4 bins), generating predictions within each bin, and plotting the performance individually.

I used the same intervention node formula for each bin, so this is consistently the same model. So, all we're looking at here is whether the model's predictions hold for different groups of participants. In contrast, I could also refit the intervention node for each bin, but it's less clear what's being modeled in that case.

```{r, message=FALSE, warning=FALSE}
# let's try creating 4 bins of participants

cutpoints <- c(.25, .5, .75, 1)
q <- quantile(interv_df %>%
                        filter(phase=="pre") %>%
                        .$diseaseSevere, cutpoints)

interv_df_binned <- interv_df %>%
  ungroup() %>%
  mutate(workerId = as.character(workerId)) %>%
  mutate(bin = ifelse(diseaseSevere <= q[1], 1,
                      ifelse( diseaseSevere <= q[2], 2,
                              ifelse(diseaseSevere <= q[3],3,
                                     4))))

bin_ids <- list(
  interv_df_binned %>% filter(phase=="pre", bin==1) %>% .$workerId,
  interv_df_binned %>% filter(phase=="pre", bin==2) %>% .$workerId,
  interv_df_binned %>% filter(phase=="pre", bin==3) %>% .$workerId,
  interv_df_binned %>% filter(phase=="pre", bin==4) %>% .$workerId
)

data_bins <- lapply(bin_ids, function(x){
  interv_df %>%
    filter(workerId %in% x)
})

bin_preds <- lapply(data_bins, function(data){

  obs_data <- d_scored %>% 
    filter(condition == "diseaseRisk") %>% 
    mutate(workerId = as.character(workerId)) %>%
    filter(workerId %in% data$workerId) %>%
    spread(phase, Mean) %>%
    mutate(score = post - pre) %>%
    group_by(scale) %>%
    summarize(
      observed = mean(score),
      std_error = stderr(score)
      )

  model <- write_jags_model(bnlearn_to_df(net.struct), d_bn)
  # model <- write_jags_model(nb_arcs, d_bn) # produces similar predictions

  # # # can modify this to test assumptions about direct effects of intervention ...
  # interv_fit <- glm(interv ~ diseaseSevere + overpar,
  #                   data = data,
  #                   family = "binomial"
  #                   )

  model <- add_node(model, glm_to_jags_eq(interv_fit))

  # can also just use "model" here so long as you include held_out_nodes
  m0 <- data %>%
    filter(phase=="pre") %>%
    .$diseaseSevere %>%
    mean()

  m1 <- data %>%
    filter(phase=="post") %>%
    .$diseaseSevere %>%
    mean()

  preds <- predict_change_scores(model,
    data.frame(interv = 0),
    data.frame(interv = 1),
    # data.frame(diseaseSevere = m0),
    # data.frame(diseaseSevere = m1),
    nodes_to_predict,
    iter = 1e5
  ) %>% mutate(interv = 0)

  preds <- process_predictions(preds, obs_data)
  }
)

```{r}
# man this is hackey ...

all_bin_preds <- bin_preds[[1]] %>%
  mutate(bin = 1) %>%
  bind_rows(
    bin_preds[[2]] %>%
      mutate(bin = 2)
      ) %>%
  bind_rows(
    bin_preds[[3]] %>%
      mutate(bin = 3)
  ) %>%
  bind_rows(
    bin_preds[[4]] %>%
  mutate(bin = 4)
  )

all_bin_preds %>%
  # filter(scale!="diseaseSevere") %>%
  ggplot(aes(x=predicted, y = observed)) +
  geom_point() +
  geom_smooth(method="lm") +
  facet_wrap(~bin, scales="fixed", ncol = 2) +
  theme_bw() +
  coord_fixed(xlim = c(-.35,.8), ylim = c(-.35,.8)) +
  theme(aspect.ratio = 1) +
  labs(title = "Predictions by quartile bin (binned on disease severity)")
```

Correlations are strongly positive in the the first 3 quartiles, and less strong in the upper-most quartile. Of course that's where we have the most restriction of range. Though the correlations are similar, note the differences in the scales, with bigger changes observed in the 1st quartile especially. The model makes essentially (exactly?) the same predictions for all four bins, so it misses in different ways across the bins.

In case it helps, here it all is together in one plot ...

```{r}
all_bin_preds %>%
  # filter(scale!="diseaseSevere") %>%
  mutate(bin = as.factor(bin)) %>%
  ggplot(aes(x=predicted, y = observed, color = bin)) +
  geom_point() +
  # facet_wrap(~bin, scales="fixed", ncol = 2) +
  theme_bw() +
  coord_fixed(xlim = c(-.35,.8), ylim = c(-.35,.8)) +
  theme(aspect.ratio = 1) +
  labs(title = "Predictions by quartile bin\n(binned on disease severity)")
```

Overall, I think this is somewhat encouraging, but it's not quite as clear or revealing as I had hoped.

# More serious model comparison

Now it's time to ask whether the differences among models are substantial and reliable enough for us to prefer any one model over another.

```{r}
all_beliefs <- nodes(net.struct)

model_compare <- tibble(
  model_name = all_beliefs,
  model = belief_targets_models
  ) %>%
    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
    mutate(scores = map(proc_preds, score_predictions_boot)) %>%
    mutate(rmse = map(scores, ~ sapply(.x, function(z){z$rmse}))) %>%
  mutate(
    mean_rmse = map_dbl(rmse, mean),
    se_rmse = map_dbl(rmse, sd)
    )

model_compare %>%
  mutate(
    UL = mean_rmse + se_rmse,
    LL = mean_rmse - se_rmse
  ) %>%
  ggplot(aes(x = model_name, y = mean_rmse, ymin = LL, ymax = UL)) +
  geom_pointrange() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

## comparing alternate structures

```{r}
# here I can swap things around
mynet <- net.struct

mynet1 <- reverse.arc(mynet, "hb","nat") # this might be the best
mynet2 <- reverse.arc(mynet, "vaccStrain","vaccDanger") 
mynet3 <- reverse.arc(mynet1, "vaccStrain","vaccDanger")
mynet4 <- reverse.arc(mynet2, "vaccTox","vaccDanger")
mynet5 <- reverse.arc(mynet3, "vaccTox","vaccDanger")

possible_dags <- list(
  mynet,
  mynet1,
  mynet2,
  mynet3,
  mynet4,
  mynet5
  )

dag_comparison_models <- lapply(possible_dags, function(dag){

  dag_model <- write_jags_model(bnlearn_to_df(dag), d_bn) %>% suppressWarnings()

  dag_model <- add_node(dag_model, glm_to_jags_eq(interv_fit))

model_names <- c(
  "original",
  "swap_hb_nat",
  "swap_vs_vd",
  "swap_hb_nat_vs_vd",
  "swap_vs_vd_vt_vd",
  "swap_hb_nat_vs_vd_vt_vd"
)

model_compare_dags <- tibble(
  model_name = model_names,
  model = dag_comparison_models
  ) %>%
    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
    mutate(proc_preds = map(predictions, process_predictions, obs_data = obs_data)) %>%
    mutate(scores = map(proc_preds, score_predictions_boot)) %>%
    mutate(rmse = map(scores, ~ sapply(.x, function(z){z$rmse}))) %>%
  mutate(
    mean_rmse = map_dbl(rmse, mean),
    se_rmse = map_dbl(rmse, sd)
    )

model_compare_dags %>%
  mutate(
    UL = mean_rmse + se_rmse,
    LL = mean_rmse - se_rmse
  ) %>%
  ggplot(aes(x = model_name, y = mean_rmse, ymin = LL, ymax = UL)) +
  geom_pointrange() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

----------------------------------------

# Broken?

Here I wrote some code to compute mse and mae across all individual subjects. I treated the resulting statistisc as means and calculated their standard error. I thought that would help clarify things, but actually it doesn't seem quite right as a model of the model predictions for average change scores. For instance, the disease severity targetting model isn't strongly preferred, despite getting like 20% more variance among average change scores.

```{r}

interv_df_wide <- interv_df %>%
  gather(scale, response, vaccIntent:parentExpert) %>%
  mutate(scale_id = paste0(scale,"_",phase)) %>%
  select(-phase, -scale, -condition, -interv) %>%
  spread(scale_id, response)

predict_change_scores_pipe <- partial(predict_change_scores,
                                      data0 = data.frame(interv=0),
                                      data1 = data.frame(interv=1),
                                      nodes_to_predict = nodes_to_predict,
                                      iter = 1e5
                                      )

compute_residuals <- function(predictions, observed){
  observed <- observed %>%
    as.matrix()

  predictions <- predictions %>% 
    select(-interv) %>%
      as.matrix()

  resids <- sweep(observed, 2, predictions)

compute_ms_residuals <- function(predictions, observed) {
  resids <- compute_residuals(predictions, observed)
  resids2 <- resids^2
  rowMeans(resids2)
}

compute_mabs_residuals <- function(predictions, observed) {
  resids <- compute_residuals(predictions, observed)
  # mae <- colMeans(abs(resids))
  rowMeans(abs(resids))
}

obs_data_indiv <- interv_df_wide %>%
            gather(scale_id, response, -workerId) %>%
          mutate(
            scale = gsub("_.*", "", scale_id),
            phase = gsub(".*_", "", scale_id)
          ) %>%
  select(-scale_id) %>%
  spread(phase, response) %>%
  mutate(change_score = post - pre) %>%
  select(-post, -pre) %>%
  spread(scale, change_score) %>%
  ungroup() %>%
  select(-workerId)

model_name_list <- c("cognitive model", "cognitive model\n(overpar)", "causal model")
model_list <- c(cog_model, cog_model2, causal_model)

model_compare <- tibble(
  model_name = model_name_list,
  model = model_list
  ) %>%
    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
    mutate(
      abs_resids = map(predictions, compute_mabs_residuals, observed = obs_data_indiv),
      resids_squared = map(predictions, compute_ms_residuals, observed = obs_data_indiv)
           ) %>%
  gather(err_type, errs, abs_resids, resids_squared) %>%
  mutate(
    mean = map_dbl(errs, mean), 
    se = map_dbl(errs, ~ sd(.x)/sqrt(length(.x)-1))
    )

```{r}
model_compare %>%
  mutate(UL = mean + se,
         LL = mean - se) %>%
  ggplot(aes(x = model_name, y = mean, ymin = LL, ymax = UL)) +
  geom_pointrange() +
  facet_wrap(~ err_type)
```

```{r}
# by individuals, not working great
all_beliefs <- nodes(net.struct)

model_compare <- tibble(
  model_name = all_beliefs,
  model = belief_targets_models
  ) %>%
    mutate(predictions = map(model, predict_change_scores_pipe)) %>%
    mutate(
      abs_resids = map(predictions, compute_mabs_residuals, observed = obs_data_indiv),
      resids_squared = map(predictions, compute_ms_residuals, observed = obs_data_indiv)
           ) %>%
  gather(err_type, errs, abs_resids, resids_squared) %>%
  mutate(
    mean = map_dbl(errs, mean), 
    se = map_dbl(errs, ~ sd(.x)/sqrt(259))
    )
```

```{r}
model_compare %>%
  mutate(UL = mean + se,
         LL = mean - se) %>%
  ggplot(aes(x = model_name, y = mean, ymin = LL, ymax = UL)) +
  geom_pointrange() +
  facet_wrap(~ err_type) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

To be completed ...
